\section{file.plt\{1,2\}}
\label{sec:plt}

This file contains stellar evolutionary properties, for one structure model
per line.  The first line contains the number of columns in the output block.
The block currently contains 81 columns, with the following contents:

\begin{enumerate}
\item JMAD, Model number
\item $t$, Age [yr] 
\item $\Delta t$, time step [yr] 
  
\item $M$, stellar mass [$M_\odot$]
\item $M_\mathrm{He}$, helium core mass [$M_\odot$] 
\item $M_\mathrm{CO}$, carbon-oxygen core mass [$M_\odot$]  
\item $M_\mathrm{ONe}$, oxygen-neon core mass [$M_\odot$]  
  
\item $\log R$, stellar radius [$R_\odot$]
\item $\log L$, stellar luminosity [$L_\odot$] 
\item $\log(T_\mathrm{eff})$, effective temperature [K] 
\item $\log T_\mathrm{c}$, central temperature [K]
\item $\log T_\mathrm{max}$, maximum temperature [K]
\item $\log \rho_\mathrm{c}$, central density [g cm$^{-3}$] 
\item $\log \rho_\mathrm{Tmax}$, density at $T=T_\mathrm{max}$ [g cm$^{-3}$] 
\item $U_\mathrm{bind}$, binding energy of H envelope [erg/($1\,\Msun$)] \footnote{Multiply with $1.9891\times10^{33}$ to get ergs. The reason for this confusing solution is that values of $10^{40-50}$\,erg don't fit in a single-precision variable, and that the value may be negative so that a log is no option.\label{fn:be}}

\item $L_\mathrm{H}$, luminosity by hydrogen burning [$L_\odot$]
\item $L_\mathrm{He}$, luminosity by helium burning [$L_\odot$]
\item $L_\mathrm{C}$, luminosity by carbon burning [$L_\odot$]
\item $L_\nu$, neutrino luminosity [$L_\odot$]
\item $L_\mathrm{th}$, luminosity by release of thermal energy [$L_\odot$]

\item $P_\mathrm{rot}$, rotational period [days] 
\item VK2, $K^2 ~\equiv~ \frac{I}{M\,R^2}$, with $I$ the moment of inertia
\item $R_\mathrm{cz}$, Depth (?) of convective envelope [$R_*$]
\item d$R_\mathrm{cz}$, Thickness (?) of convective envelope [$R_*$]
\item TET, Convective turnover timescale
\item RAF, Alfv\'en radius 
\item BP, poloidal magnetic field

\item $P_\mathrm{orb}$, orbital period [days] 
\item FLR = $^e\log\left(R_*/R_\mathrm{rl}\right)$, relative Roche Lobe Radius, also called RLF
\item F1, $\sim~\Phi_\mathrm{surf} - \Phi_\mathrm{L1}$ [erg] ?
\item $\dot{M}$, total mass loss [$M_\odot$ yr$^{-1}$]
\item $\dot{M}_\mathrm{wind}$, wind mass loss [$M_\odot$ yr$^{-1}$]
\item $\dot{M}_\mathrm{mt}$, mass transfer rate [$M_\odot$ yr$^{-1}$]
\item $H_\mathrm{orb}$, orbital angular momentum [10$^{50}$ g cm$^2$ s$^{-1}$] 
\item d$H_\mathrm{orb}/dt$, total orbital angular momentum loss rate [10$^{50}$ g cm$^2$ s$^{-2}$]
\item d$H_\mathrm{gw}/dt$, change in $H_\mathrm{orb}$ due to gravitational waves [10$^{50}$ g cm$^2$ s$^{-2}$]
\item d$H_\mathrm{wi}/dt$, change in $H_\mathrm{orb}$ due to wind mass loss [10$^{50}$ g cm$^2$ s$^{-2}$]
\item d$H_\mathrm{so}/dt$, change in $H_\mathrm{orb}$ due to spin-orbit coupling [10$^{50}$ g cm$^2$ s$^{-2}$]
\item d$H_\mathrm{ml}/dt$, change in $H_\mathrm{spin}$ due to non-conservative mass transfer [10$^{50}$ g cm$^2$ s$^{-2}$]
\item $M_\mathrm{comp}$, companion mass [$M_\odot$] 
\item $e$, orbital ellipticity

\setcounter{enumi}{41} 
\item-- \,48. Surface abundances of: 42:H, 43:He, 44:C, 45:N, 46:O, 47:Ne, 48:Mg
\setcounter{enumi}{48} 
\item-- \,55. $T_\mathrm{max}$ abundances of: 49:H, 50:He, 51:C, 52:N, 53:O, 54:Ne, 55:Mg
\setcounter{enumi}{55} 
\item-- \,62. Central abundances of: 56:H, 57:He, 58:C, 59:N, 60:O, 61:Ne, 62:Mg
\setcounter{enumi}{62} 
\item-- \,68. Convection zone boundaries (\texttt{mcb}); $> 0$: beginning, $< 0$ end of zone (max. 3 sets)
\setcounter{enumi}{68} 
\item-- \,74. Semi-convection zone boundaries (\texttt{msb}); $> 0$: beginning, $< 0$ end of zone (max. 3 sets)
\setcounter{enumi}{74} 
\item-- \,80. Nuclear energy production zone ($\varepsilon_\mathrm{nuc} > \varepsilon_\mathrm{tresh} \sim 10 L_*/M_* $) boundaries (\texttt{mex}); $> 0$: beginning, $< 0$ end of zone (max.\ 3 sets)
\setcounter{enumi}{80} 

\item $Q_\mathrm{conv}$, the mass fraction of the convective envelope

\item $P_\mathrm{c}$, central pressure [cgs]

\item $P_\mathrm{rot,c}$, rotational period in the centre [s] 
\footnote{The latest 2005 version, used at NU, has STRMDL in column 83 and column 89 as its last column.}

\item $B\!E_0$, binding energy due to gravitational energy [erg/($1\,\Msun$)] $^{\ref{fn:be}}$
\item $B\!E_1$, binding energy due to internal energy [erg/($1\,\Msun$)] $^{\ref{fn:be}}$
\item $B\!E_2$, binding energy due to recombination energy [erg/($1\,\Msun$)] $^{\ref{fn:be}}$
\item $B\!E_3$, binding energy due to $H_2$ association energy [erg/($1\,\Msun$)] $^{\ref{fn:be}}$

\item $S_\mathrm{c}$, specific entropy in core [erg g$^{-1}$ K$^{-1}$]
\item $S_{T=10^5K}$, specific entropy in the convective envelope at $T=10^5$K [erg g$^{-1}$ K$^{-1}$]

\item $R_\mathrm{He}$, radius of the helium core [$\Rsun$]
\item $R_\mathrm{CO}$, radius of the CO core [$\Rsun$]

\item STRMDL, a structure model is stored (1.0) or not (0.0)

\end{enumerate}




